E511-Signal Processing-Final Project

### 2018-12-14 paper/main.tex
Number equations and PIT detail.

To perform NMF, we transformed isolated audio samples of two speakers (speaker 1 and speaker 2) to a frequency-time representation using short-time Fourier transform (STFT) before decomposing each signal using the following iterative update rules:
\newline

$W = W \bigodot \frac{\frac{X}{WH}H^T}{1{FxT}H^T}$ \hspace{1cm} $H = H \bigodot \frac{W^T\frac{X}{WH}}{W^T1^{FxT}}$
\newline

@@

\[
\dfrac{W_{S1}H_{(1:30,:)}}
{W_{S1}H_{(1:30,:)}+W_{S2}H_{(31:60,:)}}
\]

@@

\[
\dfrac{S_{(t,f)}^2}{S_{(t,f)}^2 + N_{(t,f)}^2}
\]

@@

\[
\dfrac{Y_r S_r + Y_i S_i}{Y_r^2 + Y_i^2} +
i\dfrac{Y_r S_i - Y_i S_r}{Y_r^2 + Y_i^2}
\]

@@

\subsection{uPIT}

>>>>

To perform NMF, we transformed isolated audio samples of two speakers (speaker 1 and speaker 2) to a frequency-time representation using short-time Fourier transform (STFT) before decomposing each signal using the following iterative update rules:

\begin{equation}
\begin{array}{ll}
W = W \bigodot \frac{\frac{X}{WH}H^T}{1{FxT}H^T} &
H = H \bigodot \frac{W^T\frac{X}{WH}}{W^T1^{FxT}}
\end{array}
\end{equation}

@@

\begin{equation}
\dfrac{W_{S1}H_{(1:30,:)}}
{W_{S1}H_{(1:30,:)}+W_{S2}H_{(31:60,:)}}
\end{equation}

@@

\begin{equation}
\dfrac{S_{(t,f)}^2}{S_{(t,f)}^2 + N_{(t,f)}^2}
\end{equation}

@@

\begin{equation}
\dfrac{Y_r S_r + Y_i S_i}{Y_r^2 + Y_i^2} +
i\dfrac{Y_r S_i - Y_i S_r}{Y_r^2 + Y_i^2}
\end{equation}

@@

\subsection{PIT and uPIT}

Utterance-level Permutation Invariant Training (uPIT) is an advancement on the Permutation Invariant Training model depicted in Figure \ref{fig:pit_diagram} where the reference signals are provided to the training model as a set rather than a list by calculating the error on all permutations of the output signals and then optimizing the model on the permutation with the lowest mean squared error (MSE). A traditional approach is to minimize the MSE between the estimated masks and the ideal masks such as in

\begin{equation}
J_m = \dfrac{1}{B} \sum_{s=1}^S || \Hat{\mathbf{M}}_S - \mathbf{M}_S ||^2_F
\end{equation}

where $B = T \times N \times S$ is the count of all time-frequency units over all sources $S$ and $F$ refers to the Frobenius norm. However, to avoid issues predicting masks in silence segments and to directly calculate the error relative to the signal reconstruction, PIT and uPIT minimize the MSE between the actual signals by applying the mask to the original spectra and then calculating the error. For PIT using the PSM with complex values the cost function is

\begin{equation}
J_{psm} = \dfrac{1}{B} \sum_{s=1}^S || \Hat{\mathbf{M}}_S \odot \mathbf{R} - \mathbf{A}_S \odot \cos(\theta_y - \theta_s) ||^2_F  
\end{equation}
